---
title: "Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---


# Report Details


```{r}
articleID <- "2-10-2014" #insert the article ID code here e.g., "10-3-2015"
reportType <- "pilot" #specify whether this is the 'pilot' report or 'copilot' report
pilotNames <- "Leili Mortazavi" #insert the pilot's name here e.g., "Tom Hardwicke".
copilotNames <- "Lily Steyer" #insert the co-pilot's name here e.g., "Michael Frank".
pilotTTC <- 240 #insert the pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
copilotTTC <- NA #insert the co-pilot's estimated time to complete (in minutes, it is fine to approximate) e.g., 120
pilotStartDate <- "11/03/19" #insert the piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
copilotStartDate <- NA #insert the co-piloting start date in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
completionDate <- "11/10/19" #insert the date of final report completion in US format e.g., as.Date("01/25/18", format = "%m/%d/%y")
```

------

#### Methods summary: 

135 undergraduates were asked to create time capsules for 9 recent experiences. For each item, they rated the level of curiousity, surprise, interest, and meaningfulness they think they would feel a few months later. 

After 3 months, participants rated how curious and surprised they predicted to be after opening each time capsule. After reading it, they rate how meaningful and interesting they actually thought it was. At this time, 106 participants responded. 

Researchers compared how accurate individuals were in predicting how they would feel about their current experiences 3 months later. 

------

#### Target outcomes: 

For this article you should focus on the findings reported in the results section for Study 1 (and Table 1).

Specifically, you should attempt to reproduce all descriptive and inferential analyses reported in the text below and associated tables/figures:

> Table 1 provides descriptive statistics for each measure
for Study 1.

> Participants' Time 1 predictions of their curiosity (M = 3.99, SD = 1.32) were lower than their actual curiosity ratings at Time 2, immediately before reading their responses (M = 4.34, SD = 1.25), t(105) = 2.88, p = .005, d = 0.27. Participants also underestimated how interesting they would find their responses. Predictions of interest at Time 1 (M = 3.54, SD = 1.01) were lower than ratings of actual interest experienced at Time 2 (M = 3.82, SD = 0.89), t(105) = 3.10, p = .003, d = 0.29.

**Note**
Make sure to use the original article for additional context and information about any necessary pre-processing steps. Also check for additional supplementary materials that may provide supporting documentation for analysis procedures.

------


```{r global_options, include=FALSE}
# sets up some formatting options for the R Markdown document
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

# Step 1: Load packages and prepare report object


```{r}
# load packages
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(ReproReports) # custom reporting functions
library(magrittr)
library(gmodels)
```


```{r}
# Prepare report object. This will be updated automatically by the reproCheck function each time values are compared
reportObject <- data.frame(dummyRow = TRUE, reportedValue = NA, obtainedValue = NA, valueType = NA, percentageError = NA, comparisonOutcome = NA, eyeballCheck = NA)
```

# Step 2: Load data

```{r importing data}
library(haven)
data <- read_sav("data/Study1_Data.sav")
```

```{r inspecting the data}
colnames(data)
```


```{r checking number of participants}
data
```

The number of rows here (135) is consistent with the number of participants at T1 reported in the paper. 

Now let's see if the number of participants who completed T2 is also consistent with what is reported in the paper (106).


```{r excluding only those who did not finish T2}
data_complete <- data %>% subset(T2_Finished == 1)
data_complete
```

Yes! The number of rows here after excluding those who didn't finish T2 is also 106. 

# Step 3: Tidy data

```{r}
data_long <- data %>% 
  mutate(Participant = seq.int(nrow(data))) %>% #adding a column for participant number 
  mutate(Completed = T2_Finished) %>%  #changinf the name of 'T2_finished' to 'Completed' 
  select(Participant, Age, Gender, Year_born, Order, Completed, Interest_composite_diff, Curious_diff, everything())
```


# Step 4: Run analysis

## Pre-processing

```{r excluding only those who did not finish time2}
data_complete <- data %>% subset(T2_Finished == 1)
data_complete
```

Yes! The number of rows here after excluding those who didn't finish T2 is also 106. 


## Descriptive statistics

###T1

***Curiosity***

```{r T1 curiosity}
mean_T1_curious <- mean(data_complete$T1_Curious)
#ci is from the package gmodels
library(gmodels)
ci_T1_curious <- ci(data_complete$T1_Curious, confidence = 0.95)
T1_curiosity <- c(round(c(mean_T1_curious, ci_T1_curious[2], ci_T1_curious[3]), digits = 2))
T1_curiosity
```

These values are consistent with the paper. 

***Surprise***

```{r T1 Surprise}
mean_T1_Surprise <- mean(data_complete$T1_Surprised)
#ci is from the package gmodels
ci_T1_Surprise <- ci(data_complete$T1_Surprised, confidence = 0.95)
T1_Surprise <- c(round(c(mean_T1_Surprise, ci_T1_Surprise[2], ci_T1_Surprise[3]), digits = 2))
T1_Surprise
```


These values are consistent with the paper.

***Meaningfulness***

```{r T1 meaningfulness}
mean_T1_meaningfulness <- mean(data_complete$T1_Meaningful)
#ci is from the package gmodels
ci_T1_meaningfulness <- ci(data_complete$T1_Meaningful, confidence = 0.95)
T1_meaningfulness <- c(round(c(mean_T1_meaningfulness, ci_T1_meaningfulness[2], ci_T1_meaningfulness[3]), digits = 2))
T1_meaningfulness
```


These values are consistent with the paper.



***Interest***

```{r T1 interest}
mean_T1_interest <- mean(data_complete$T1_Interesting)
#ci is from the package gmodels
ci_T1_interest <- ci(data_complete$T1_Interesting, confidence = 0.95)
T1_interest <- c(round(c(mean_T1_interest, ci_T1_interest[2], ci_T1_interest[3]), digits = 2))
T1_interest
```


These values are consistent with the paper.


***Interest (composite)***

```{r T1 composite interest}
mean_T1_interest_comp <- mean(data_complete$T1_Interest_Composite)
#ci is from the package gmodels
ci_T1_interest_comp <- ci(data_complete$T1_Interest_Composite, confidence = 0.95)
T1_interest_comp <- c(round(c(mean_T1_interest_comp, ci_T1_interest_comp[2], ci_T1_interest_comp[3]), digits = 2))
T1_interest_comp
```


These values are consistent with the paper.

###T2

***Curiosity***

```{r T2 curiosity}
mean_T2_curious <- mean(data_complete$T2_Curious)
#ci is from the package gmodels
ci_T2_curious <- ci(data_complete$T2_Curious, confidence = 0.95)
T2_curiosity <- c(round(c(mean_T2_curious, ci_T2_curious[2], ci_T2_curious[3]), digits = 2))
T2_curiosity
```

These values are consistent with the paper. 

***Surprise***

```{r T2 Surprise}
mean_T2_Surprise <- mean(data_complete$T2_Surprised)
#ci is from the package gmodels
ci_T2_Surprise <- ci(data_complete$T2_Surprised, confidence = 0.95)
T2_Surprise <- c(round(c(mean_T2_Surprise, ci_T2_Surprise[2], ci_T2_Surprise[3]), digits = 2))
T2_Surprise
```


These values are consistent with the paper.

***Meaningfulness***

```{r T2 meaningfulness}
mean_T2_meaningfulness <- mean(data_complete$T2_Meaningful)
#ci is from the package gmodels
ci_T2_meaningfulness <- ci(data_complete$T2_Meaningful, confidence = 0.95)
T2_meaningfulness <- c(round(c(mean_T2_meaningfulness, ci_T2_meaningfulness[2], ci_T2_meaningfulness[3]), digits = 2))
T2_meaningfulness
```


These values are consistent with the paper.



***Interest***

```{r T2 interest}
mean_T2_interest <- mean(data_complete$T2_Interesting)
#ci is from the package gmodels
ci_T2_interest <- ci(data_complete$T2_Interesting, confidence = 0.95)
T2_interest <- c(round(c(mean_T2_interest, ci_T2_interest[2], ci_T2_interest[3]), digits = 2))
T2_interest
```


These values are consistent with the paper.


***Interest (composite)***

```{r T2 composite interest}
mean_T2_interest_comp <- mean(data_complete$T2_Interest_Composite)
#ci is from the package gmodels
ci_T2_interest_comp <- ci(data_complete$T2_Interest_Composite, confidence = 0.95)
T2_interest_comp <- c(round(c(mean_T2_interest_comp, ci_T2_interest_comp[2], ci_T2_interest_comp[3]), digits = 2))
T2_interest_comp
```


These values are consistent with the paper.

###T2 - T2

```{r}

```



***Curiosity***

```{r T2 - T1 curiosity}
mean_curious_diff <- mean(data_complete$Curious_diff)
#ci is from the package gmodels
ci_curious_diff <- ci(data_complete$Curious_diff, confidence = 0.95)
curiosity_diff <- c(round(c(mean_curious_diff, ci_curious_diff[2], ci_curious_diff[3]), digits = 2))
curiosity_diff
```

These values are consistent with the paper. 

***Surprise***

Since there's no column for Surprise_diff, Meaningful_diff, and Interest_diff, I'll make those below:

```{r adding diff columns}
data_complete <- data_complete %>% 
  mutate(Surprised_diff = T2_Surprised - T1_Surprised, 
         Meaningful_diff = T2_Meaningful - T1_Meaningful, 
         Interesting_diff = T2_Interesting - T1_Interesting)
```


```{r T2 - T1 Surprise}
ci_Surprise_diff <- ci(data_complete$Surprised_diff, confidence = 0.95)
surprise_diff <- c(round(c(mean(data_complete$Surprise_diff), ci_Surprise_diff[2], ci_Surprise_diff[3]), digits = 2))
surprise_diff
```


These values are consistent with the paper.

***Meaningfulness***

```{r T2 - T1 meaningfulness}
ci_meaning_diff <- ci(data_complete$Meaningful_diff, confidence = 0.95)
meaning_diff <- c(round(c(mean(data_complete$Meaningful_diff), ci_meaning_diff[2], ci_meaning_diff[3]), digits = 2))
meaning_diff
```


These values are consistent with the paper.



***Interest***

```{r T2 - T1 interest}
ci_interest_diff <- ci(data_complete$Interesting_diff, confidence = 0.95)
interest_diff <- c(round(c(mean(data_complete$Interesting_diff), ci_interest_diff[2], ci_interest_diff[3]), digits = 2))
interest_diff
```


These values are consistent with the paper.


***Interest (composite)***

```{r T2 - T1 interest composite}
ci_interest_comp_diff <- ci(data_complete$Interest_composite_diff, confidence = 0.95)
interest_comp_diff <- c(round(c(mean(data_complete$Interest_composite_diff), ci_interest_comp_diff[2], ci_interest_comp_diff[3]), digits = 2))
interest_comp_diff
```


These values are consistent with the paper.


##Inferential stats

###Curiosity

```{r t-test curiosity}
t_curiosity <- t.test(data_complete$T2_Curious, y = data_complete$T1_Curious, paired = TRUE)
t_curiosity
p_curiosity <- t_curiosity[3] 
```

Results are consistent with the paper. 

```{r effect size curiosity}
d_curious <- (mean_T2_curious - mean_T1_curious)/sd(c(data_complete$T2_Curious, data_complete$T1_Curious)) 
d_curious
```

Results are consistent with the paper.

###Surprise

```{r t-test surprise}
t_surprise <- t.test(data_complete$T2_Surprised, y = data_complete$T1_Surprised, paired = TRUE)
t_surprise
p_surprise <- t_surprise[3]
```

###Meaningfulness

```{r t-test meaning}
t_meaning <- t.test(data_complete$T2_Meaningful, y = data_complete$T1_Meaningful, paired = TRUE)
t_meaning
p_meaning <- t_meaning[3]
```

Results are consistent with the paper. 

###Interest

```{r t-test interest}
t_interest <- t.test(data_complete$T2_Interesting, y = data_complete$T1_Interesting, paired = TRUE)
p_interest <- t_interest[3]
t_interest
```

Results are consistent with the paper. 

###Interest (composite)

```{r t-test interest composite}
t_interest_comp <- t.test(data_complete$T2_Interest_Composite, y = data_complete$T1_Interest_Composite, paired = TRUE)
p_interest_comp <- t_interest_comp[3]
t_interest_comp
```

Results are consistent with the paper. 

```{r effect size interest composite}
d_interest <- (mean_T2_interest_comp - mean_T1_interest_comp)/sd(c(data_complete$T2_Interest_Composite, data_complete$T1_Interest_Composite)) 
d_interest
```

Seems like the paper always rounds up to 2 digits, but here they report d = 0.29, which is not rounding up that would have returned d = 0.30.


# Step 5: Conclusion

All results were consistent with the reported findings in the paper. Here's a table similar to Table 1 in the original paper:

"Time 1 95% CI (lower)", "Time 1 95% CI (higher)"
```{r table 1}
table1 <- matrix(
  c(T1_curiosity, T2_curiosity, curiosity_diff, p_curiosity, 
    T1_interest_comp, T2_interest_comp, interest_comp_diff, p_interest_comp,
    T1_Surprise, T2_Surprise, surprise_diff, p_surprise,
    T1_meaningfulness, T2_meaningfulness, meaning_diff, p_meaning,
    T1_interest, T2_interest, interest_diff, p_interest), 
  ncol = 10)

colnames(table1) <- c("T1 mean", "T1 95% CI (lower)", "T1 95% CI (higher)", "T2 mean", "T2 95% CI (lower)", "T2 95% CI (higher)", "T2-T1 mean", "T2-T1 95% CI (lower)", "T2-T1 95% CI (higher)", "p")
rownames(table1) <- c("Curiosity", "Interest (composite)", "Surprise", "Meaningfulness", "Interest")
table1_df <- as.data.frame(table1) 
table1_df
```


```{r making table 1 pretty}
library(formattable)
table1_pretty <- formattable(table1_df)
table1_pretty
```



```{r}
reportObject <- reportObject %>%
  filter(dummyRow == FALSE) %>% # remove the dummy row
  select(-dummyRow) %>% # remove dummy row designation
  mutate(articleID = articleID) %>% # add variables to report 
  select(articleID, everything()) # make articleID first column

# decide on final outcome
if(any(reportObject$comparisonOutcome %in% c("MAJOR_ERROR", "DECISION_ERROR"))){
  finalOutcome <- "Failure"
}else{
  finalOutcome <- "Success"
}

# collate report extra details
reportExtras <- data.frame(articleID, pilotNames, copilotNames, pilotTTC, copilotTTC, pilotStartDate, copilotStartDate, completionDate, finalOutcome)

# save report objects
if(reportType == "pilot"){
  write_csv(reportObject, "pilotReportDetailed.csv")
  write_csv(reportExtras, "pilotReportExtras.csv")
}

if(reportType == "copilot"){
  write_csv(reportObject, "copilotReportDetailed.csv")
  write_csv(reportExtras, "copilotReportExtras.csv")
}
```

# Session information

[This function will output information about the package versions used in this report:]

```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
